(An introduction to )MultiSymplectic Geometry and Classical Field systems

### 2019-03-01 ms-mechanics.tex

\title{(An introduction to )MultiSymplectic Geometry and Classical Field systems}
\author{
	International Ph.D. Program in "Science" \\
	"Differential geometry and applications to modern physics" \\
	Department of Mathematics and Physics\\
	Universit\'a Cattolica del Sacro Cuore\\
	via Musei 41, 25121 Brescia, \underline{Italy}
}

@@

\begin{abstract}
$n$-plectic structures (also called \emph{multisymplectic}) are a rather straightforward generalization of symplectic ones where closed non-degenerate $n+1$-forms take the place of  $2$-forms.
\\
As the same way as one can relate a symplectic manifold to any ordinary classical mechanical system (e.g. a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (think them as a continuum medium like a filament or a membrane).
\\
The aim of my talk is to give an account on the multisymplectic framework for (I-order) classical fields theories comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
\\
Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allow us to treat such formal object in a finite dimensional setting.

>>>>

\title{(An introduction to )MultiSymplectic Geometry and Classical Field systems}
\author{
	International Ph.D. Program in "Science" \\
	"Differential geometry and applications to modern physics" \\
	%
	\begin{minipage}[c]{0.5\textwidth}
		\vspace{2em}
		\centering
		Department of Mathematics and Physics\\
		Universit\'a Cattolica del Sacro Cuore\\
		via Musei 41, 25121 Brescia, \underline{Italy}
	\end{minipage}
	\hfill
	\begin{minipage}[c]{0.5\textwidth}
		\vspace{2em}
		\centering
		Department of Mathematics\\
		KU Leuven\\
		Celestijnenlaan 200B, 3001 Leuven, \underline{Belgium}
	\end{minipage}
}

@@

\begin{abstract}
$n$-plectic structures (also called \emph{multisymplectic}) are a rather straightforward generalization of symplectic ones where closed non-degenerate $n+1$-forms take the place of  $2$-forms.
\\
Just as one can associate a symplectic manifold to an ordinary classical mechanical system (e.g. a single point-like particle constrained to some manifold), it is possible to associate a multisymplectic manifold to any classical field systems (e.g. a continuous medium like a filament or a membrane).
\\
The aim of this talk is to give an account on the multisymplectic framework for (I-order) classical fields theories trying to comparing it with another object that plays a significant role in the mathematical description of classical fields called \emph{Covariant phase space}.
\\
Being the latter a sort of "$\infty$-dimensional manifold" (namely a mapping space), we will draw from this picture the idea that multisymplectic geometry could be seen as a tool that allows us to treat such formal object in a finite-dimensional setting.
